---
title: "RTweet"
author: "Rochelle Terman"
date: "2021"
output: html_document
---


## Collecting Twitter Data with `RTweet`

Twitter actually has two separate APIs:

1. The __REST API__ allows you to read and write Twitter data. For research purposes, this allows you to search the recent history of tweets and look up specific users.
2. The __Streaming API__ allows you to access public data flowing through Twitter in real-time. It requires your R session to be running continuously, but allows you to capture a much larger sample of tweets while avoiding rate limits for the REST API.

There are several packages for R for accessing and searching Twitter. In this unit, we'll practice using the `RTweet` library, which allows us to easily collect data from Twitter's REST and stream APIs.

### What is in `Rtweet`?

`Rtweet` is a plug-and-play R package that allows you to easily access Twitter's REST and streaming APIs
And it's free! All you need is a Twitter account to get started.

* Collection of functions to access data from Twitter
    * Let's quickly look at [the documentation](https://cran.r-project.org/web/packages/rtweet/rtweet.pdf) 
    * Some useful functions: `get_timeline`, `search_tweets`, `search_users`
    
* Shortcomings:
    * Finite amount of data you can pull
    * Challenges for reproducible code: every time you run, you’ll get different results

### Setting up `RTweet`

To use `RTweet`, follow these steps:

1. If you don't have a Twitter account, create one [here](https://twitter.com/i/flow/signup).
2. Install the `RTweet` package from CRAN.
2. Load the package into R.
3. Send a request to Twitter's API by calling any of the package's functions, like `search_tweets` or `get_timeline`.
4. Approve the browser popup (to authorize the `rstats2twitter` app).
5. Now, you're ready to use RTweet!

Let's go ahead and load `RTweet` along with some other helpful packages:

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(rtweet)
library(lubridate)
library(kableExtra)
```

### UChicago Political Science Prof Tweets

Let's explore the `RTweet` package to see what we can learn about the tweeting habits of UChicago Political Science faculty.

The function `get_timeline` will pull the most recent `n` number of tweets from a given handle(s). To pull tweets from multiple handles, write out a vector of the handles in the `user` argument.

Let's pull tweets from five faculty members in the department.

```{r}
profs <- get_timeline(
  user = c("carsonaust", "profpaulpoast", "pstanpolitics", "rochelleterman", "bobbygulotty"),
  n = 1000
)
kable(head(profs))
```

Now, let's visualize which professors are tweeting the most, by week.

```{r, warning=FALSE}
profs %>%
  group_by(screen_name) %>%
  mutate(created_at = as.Date(created_at)) %>%
  filter(created_at >= "2021-01-01") %>%
  ts_plot(by = "week")
```


### Hashtags and Text Strings

We can also use `RTweet` to explore certain hashtags or text strings.

Let's use Duke Ellington as an example -- we can use `search_tweets` to pull the most recent n number of tweets that include the hashtag `#DukeEllington` or the string `"Duke Ellington"`.

#### Hashtag Challenge {-}

Using the documentation for `search_tweets` as a guide, try pulling the 2,000 most recent tweets that include `#DukeEllington` or `"Duke Ellington"` -- be sure to exclude retweets from the query.

1. Why didn't your query return 2,000 results?

2. Identify the user that has used either the hashtag or the string in the greatest number of tweets -- where is this user from?

```{r, message=FALSE}
duke <- search_tweets(
  q = '#DukeEllington OR "Duke Ellington"',
  n = 2000,
  include_rts = FALSE
)

duke %>%
  count(user_id, location) %>%
  arrange(desc(n))
```

