---
title: "Selenium"
author: "3I: Webscraping and Data Management in R"
date: "Aug 2020"
output:
  html_document: default
  pdf_document: default
---

## Selenium

Selenium is an umbrella project focused on [automating web browsers](https://www.selenium.dev/documentation/en/). 

Selenium comprises many different tools, libraries, and APIs. But the basic goal is **web browser automation**: writing code to remotely control a web browser (e.g. Chrome, Firefox) as if we were a real user surfing the web. With Selenium, we can enter text into fields, select drop-down menus, check boxes, and click on links.

Selenium is used primarily for front-end testing of websites. But we can also use it to level up our webscraping game. So far, we've been using `RVest` to read static HTML from a URL. In other words, we never had to open an actual browser. But what if that site uses javascript to dynamically display HTML on the single URL 

To use Selenium, we need to run a Selenium Server, written in Java, that controls the browser on our computer. The package `RSelenium` allows us to connect to this server from within `R`. RSelenium provides R bindings (i.e., translation code) for accessing a Selenium **Webdriver**. 

`RSelenium` features a nice vignette, available [here.](https://docs.ropensci.org/RSelenium/articles/basics.html)

```{r}
library(RSelenium)
library(wdman)
library(tidyverse)
library(rvest)

# Start a selenium server and browser
rD <- rsDriver(browser = "firefox")
remDr <- rD[["client"]]

# check status
remDr$getStatus()

# navigate
remDr$navigate("http://www.google.com")
```

### Scraping election data from West Bengal 

```{r}
remDr$navigate("http://wbsec.gov.in/results/panchayat_election_detailed_result?election_year=2013")
```

Why can't we scrape this site using `RVest`?

### Selecting from the `District` Menu

In order to select from a drop-down menu, we need to go through 2 steps:

1. Click on the **menu.**

We can use the method `findElements` to find an element on the page by its name. An easy way to do this is to inspect the element.

```{r}
# find "district" drop down
district <- remDr$findElement(using = "name", value = "zilla_parishad")

class(district)
?webElement

district$getElementText()
district$clickElement()
```

2. Click on the **option.**

Now if we want to get the different options in this drop down, we can do the same. You'll notice that each name is associated with a unique value.

```{r}
# find options in that drop down
district$selectTag() #returns options

# store all elements for options
district_options = district$findChildElements(using = "css selector", value = "option")

# get first option
district_first <- district_options[[2]]
district_name <- district_first$getElementText()[[1]]

# click on that
district_first$clickElement()
```

### Challenge 1: Selecting from the `Polling Data` Menu

Fill in the code chunk below to select the first option from the  "Polling Date" drop down.

```{r}
# YOUR CODE HERE

# find "polling" drop down
polling <- remDr$findElement(using = "name", value = "election_date")
# find options
polling_options = polling$findChildElements(using = "css selector", value = "option")
# get first
polling_first <- polling_options[[2]]
# click on that
polling_first$clickElement()
```

### Getting the results

Let's click "submit" to get the results:

```{r}
submit <- remDr$findElement(using = "name", value = "submit")
submit$clickElement()
```

Our selections brought us to a table. Now let's get the underlying html. First we'll identify it by its CSS selector, and then use the `getPageSource` method.

```{r}
# select the table element
table = remDr$findElement(using = "class", value = "table_data")

# extract html
table_html <- table$getPageSource()
```

To parse the html, we'll use `RVest`:

```{r}
# read HTML
table_html <- read_html(table_html[[1]])

# handy-dandy function to parse html tables into dataframes -- and it's vectorized!
table_dfs <- html_table(table_html, fill = F)

# let's check it out
knitr::kable(table_dfs[[1]])
```

### Parsing the tables

What a mess! They should have taken my data management course. Let's use our `tidyverse` skills to clean this up.

```{r}
# do it with just one table.
a_table <- table_dfs[[1]]

# make election_level database
election_level <- a_table %>%
  select(`Seat Name`:`Votes Rejected`) %>%
  mutate(District = district_name) %>%
  head(1)

# make candidate_level database
candidate_level <- a_table %>%
  select(`Seat Name`, OSN:`Vote Secured`) %>%
  mutate(District = district_name,
         `Seat Name` = `Seat Name`[1])
```

Let's transform this code into a function and apply it to all the tables.

```{r}
# make functions and loop
parse_election <- function(table_i) {
  
  # make election_level database
  election_level <- table_i %>%
    select(`Seat Name`:`Votes Rejected`) %>%
    mutate(District = district_name) %>%
    head(1)
  
  return(election_level)
}

parse_candidates <- function(table_i) {
  
  # make candidate_level database
  candidate_level <- table_i %>%
    select(`Seat Name`, OSN:`Vote Secured`) %>%
    mutate(District = district_name,
           `Seat Name` = `Seat Name`[1])
  
  return(candidate_level)
}
  
elections <- map_dfr(table_dfs, parse_election)
candidates <- map_dfr(table_dfs, parse_candidates)
```

### Challenge 2

Using the code above as a guide, write a program that loops through all the options in the `Distrct` menu, grabs the results, and parses the data into a tidy dataframe.

```{r}
# write function to automate menu selection
select_district <- function(option_i){
  
  remDr$navigate("http://wbsec.gov.in/results/panchayat_election_detailed_result?election_year=2013")
  
  Sys.sleep(2)
      
  # select "district" option
  district <- remDr$findElement(using = "name", value = "zilla_parishad")
  district_options = district$findChildElements(using = "css selector", value = "option")
  district_selection <- district_options[[1 + option_i]]
  district_name <- district_selection$getElementText()[[1]]
  district_selection$clickElement()
  
  Sys.sleep(2)
  
  # find "polling" drop down
  polling <- remDr$findElement(using = "name", value = "election_date")
  polling_options = polling$findChildElements(using = "css selector", value = "option")
  polling_selection <- polling_options[[2]]
  polling_selection$clickElement()
  
  # click
  submit <- remDr$findElement(using = "name", value = "submit")
  submit$clickElement()
  
  Sys.sleep(2)
  
  # get tables
  table = page$findElement(using = "class", value = "table_data")
  
  # extract html
  table_html <- table$getPageSource()
  
  # read HTML
  table_html <- read_html(table_html[[1]])
  
  # parse html tables into dataframes
  table_dfs <- html_table(table_html, fill = F)
  
  # tidy data
  elections <- map_dfr(table_dfs, parse_election)
  candidates <- map_dfr(table_dfs, parse_candidates)
  
  # staple into a list
  data_list <- list(Elections = elections, Candidates = candidates)
  
  return(data_list)
}

# get data for second option
p2 <- select_district(2)
```
